---
title: "NGCHM Support Files Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{onLoad}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package provides two files required by the 'NGCHM' package to export Next-Generation Heat Maps (NG-CHMs):

1. **ShaidyMapGen.jar**: A Java program used by `NGCHM::chmExportToFile()`, `NGCHM::chmExportToHTML()`, and
   `NGCHM::chmExportToPDF()`.
2. **ngchmWidget-min.js**: A JavaScript file used by `NGCHM::chmExportToHTML()`

When loading 'NGCHMSupportFiles', the paths to these files are set in the environment variables:

1. **SHAIDYMAPGEN**: The path to ShaidyMapGen.jar in NGCHMSupportFiles
2. **NGCHMWIDGETPATH**: The path to ngchmWidget-min.js in NGCHMSupportFiles

NGCHMSupportFiles can be installed from our R-Universe repository:

```{r setup}
install.packages('NGCHMSupportFiles', repos = c('https://md-anderson-bioinformatics.r-universe.dev', 'https://cloud.r-project.org'))
library(NGCHMSupportFiles)
```
